---
title: "WRCA Courses"
format: html
---

```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
library(ggplot2)
library(readr)
library(here)
library(dplyr)
library(DescTools)
library(TraMineR)
library(tidyr)
library(markovchain)

# load in data
wrca_frame <- read_csv(
  here("data", "wrca_audit.csv"),
  show_col_types = FALSE
  ) |>
  mutate(rep_verb = case_when(rep_verb == "reaad" ~ "read",
                              rep_verb == "NOT YET COMPLETE" ~ NA,
                              rep_verb == "complete" ~ NA,
                              rep_verb == "visit" ~ "read",
                              rep_verb == "view" ~ "read",
                              rep_verb == "research" ~ "read",
                              TRUE ~ rep_verb)) |>
  mutate(rep_object = case_when(rep_object == "assiggnment" ~ "assignment",
                                rep_object == "article" ~ "text",
                                rep_object == "document" ~ "text",
                                rep_object == "chapter" ~ "text",
                                rep_object == "images" ~ "image",
                                rep_object == "diagram" ~ "image",
                                rep_object == "interview" ~ "text",
                                rep_object == "museum" ~ "website",
                                rep_object == "musuem" ~ "website",
                                rep_object == "university" ~ "website",
                                rep_object == "videos" ~ "video",
                                rep_object == "chapter" ~ "text",
                                rep_object == "webpage" ~ "website",
                                TRUE ~ rep_object)) |>
  mutate(exp_verb = case_when(exp_verb == "comlpete" ~ "complete",
                              exp_verb == "?" ~ NA,
                              exp_verb == "revise" ~ "modify",
                              exp_verb == "solve" ~ "complete",
                              exp_verb == "answer" ~ "complete",
                              TRUE ~ exp_verb)) |>
  mutate(exp_object = case_when(exp_object == "collage (vision board)" ~ "collage",
                                exp_object == "definion" ~ "definition",
                                exp_object == "question" ~ "questions",
                                exp_object == "slides" ~ "presentation",
                                TRUE ~ exp_object)) |>
  mutate(dok = case_when(dok == "Assignment Missing?" ~ NA,
                              dok == "Not sure; can't see the full activity since it is a Google Form" ~ NA,
                              TRUE ~ dok)) |>
  arrange(course, lesson, sequence)
```

## Overview

This is a very brief look at **a sample of WRCA courses**. Examined first is the
general structure of the courses, including the *number of lessons per course* and 
*number of activities per lesson*.

The next section examines the Universal Design for Learning attributes, particularly
around providing multiple modes of representation and expression. Examined are a
coded list of *verbs* and a coded list of *media* with which students are expected
to engage.

The final section examines the depth of knowledge attributed to each activity. 
Provided are the *distribution of DOK* and some explorations of *relationships between DOK and number of lessons*,
*number of activities*, and *sequence of activities*.

## Course Structures

### Number of Lessons per Course

```{r lesson-distribution}
wrca_lessons <- wrca_frame |>
  select(course, lesson) |>
  na.omit() |>
  group_by(course) |>
  filter(lesson == max(lesson)) |>
  ungroup() |>
  unique() |>
  arrange(lesson, course)
Desc(wrca_lessons$lesson, plotit = TRUE, main = "Lessons per Course")
```

### Number of Activities per Lesson

```{r activity-distribution}
wrca_activities <- wrca_frame |>
  select(course, lesson, sequence) |>
  na.omit() |>
  group_by(course, lesson) |>
  filter(sequence == max(sequence)) |>
  ungroup() |>
  arrange(course, lesson)
Desc(wrca_activities$sequence, main = "Number of Activities Per Lesson", plotit = TRUE)
```

## Indicators of Universal Design for Learning

### Verbs Used for Representation

```{r rep-verbs}
Desc(wrca_frame$rep_verb, plotit = TRUE, main = "Representation Verbs")
```

### Media Used for Representation

```{r rep-media}
Desc(wrca_frame$rep_object, plotit = TRUE, main = "Representation Media")
```

### Verbs Used for Expression

```{r exp-verbs}
Desc(wrca_frame$exp_verb, plotit = TRUE, main = "Expression Verbs")
```

### Media Used for Expression

```{r exp-media}
Desc(wrca_frame$exp_object, plotit = TRUE, main = "Expression Media")
```

## Depth of Knowledge

### Depth of Knowledge for Activities

```{r dok-distribution}
wrca_frame$dok <- factor(wrca_frame$dok, level = c("1", "2", "3", "4"))
Desc(wrca_frame$dok, plotit = TRUE, main = "Depth of Knowledge")
```

### Depth of Knowledge Sequences

The probability that one DOK will be followed by another.

```{r markov}
markovchainFit(wrca_frame$dok)$estimate
```

### Number of Lessons and Average Depth of Knowledge
```{r noldok, warning=FALSE, message=FALSE}
nol_frame <- wrca_frame |>
  select(course, lesson, dok) |>
  na.omit() |>
  group_by(course) |>
  filter(lesson == max(lesson)) |>
  mutate(dok = median(as.integer(dok))) |>
  ungroup() |>
  unique() |>
  mutate(dok = factor(dok, levels = c("1", "2", "3", "4")))

Desc(lesson ~ dok, nol_frame, main = "Number of Lessons and DOK")
```

### Number of Activities and Average Depth of Knowledge

```{r noadok, warning=FALSE, message=FALSE}
noa_frame <- wrca_frame |>
  select(course, lesson, sequence, dok) |>
  na.omit() |>
  group_by(course, lesson) |>
  filter(sequence == max(sequence)) |>
  mutate(dok = median(as.integer(dok))) |>
  ungroup() |>
  unique() |>
  mutate(dok = factor(dok, levels = c("1", "2", "3", "4"))) |>
  mutate(sequence = as.integer(sequence))

Desc(sequence ~ dok, noa_frame, main = "Number of Activities and DOK")
```

### Sequence and Depth of Knowledge

Does the *activity sequence* impact the identified *depth of knowledge*?

```{r sdok, warning=FALSE, message=FALSE}
wrca_frame$sequence <- factor(wrca_frame$sequence,
                              levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11"))
wrca_frame$dok <- as.integer(wrca_frame$dok)

Desc(sequence ~ dok, wrca_frame, plotit = TRUE, main = "Sequence and Depth of Knowledge")
```

```{r noadok2, message=FALSE, warning=FALSE}
noa2_frame <- wrca_frame |>
  select(course, lesson, sequence, dok) |>
  na.omit() |>
  group_by(course, lesson, sequence) |>
  filter(dok == max(as.numeric(dok))) |>
  ungroup() |>
  unique() |>
  pivot_wider(names_from = sequence, values_from = dok, names_prefix = "activity_")

dok.alphab <- c("1", "2", "3", "4")
dok.seq <- seqdef(noa2_frame, 3:13, xtstep = 1, alphabet = dok.alphab)
seqIplot(dok.seq, border = NA, with.legend = "right")

trate <- seqtrate(dok.seq)
knitr::kable(round(trate, 2))

seqHtplot(dok.seq, with.legend = "right", legend.prop=0.4)
```

## Session Information {.appendix}

Session information is provided for reproducibility purposes.

```{r print-session-info, purl=FALSE}
sessioninfo::session_info(pkgs = "attached")
```